Instructions for \confname{} Proceedings

### 2019-05-08 papers/EMNLP2019/analysis.tex
new table in analysis with relation distr. shown for each domain

\begin{table}

\begin{tabular}{lll}
\toprule
       relation &  types & tokens \\
\midrule
synonymy &  0.01 &  0.09 \\
co-hyponymy &  0.03 &  0.07 \\
hypernymy &  0.06 &  0.35 \\
not-covered &  0.19 &  0.04 \\
crossclassified &  0.70 &  0.47 \\
\bottomrule
\end{tabular}
% \small
% \begin{tabular}{llll}
% \toprule
%         relation & \% types & \% tokens & av. depth \\
% \midrule
%  co-hyponymy (closure, max depth=10) &  0.889 &  0.551 &       3.479 \\
%     hyponymy (closure, max depth=10) &  0.097 &  0.328 &       2.204 \\
%         synonymy &  0.015 &  0.121 &       1.000 \\
% \bottomrule
% \end{tabular}
\caption{Lexical relations between naming variants according to WordNet, for the set of name pairs where both words can be found in WordNet and stand in a \sz{should we produce this table for the different domains?} \gbt{yes, please. Maybe do rows domains, columns lexical relations (synymymy, hyponymy, co-hyponymy, other, not in wordnet), with subcolumns for types and tokens? And do percentages over rows -- for each domain, how many of the variants we find fall into each of the classes. This way we'll be able to see differences across domains.}}
\label{tab:rel}
\end{table}

>>>>

\begin{table*}

%\begin{tabular}{lll}
%\toprule
%       relation &  types & tokens \\
%\midrule
%synonymy &  0.01 &  0.09 \\
%co-hyponymy &  0.03 &  0.07 \\
%hypernymy &  0.06 &  0.35 \\
%not-covered &  0.19 &  0.04 \\
%crossclassified &  0.70 &  0.47 \\
%\bottomrule
%\end{tabular}
% \small
% \begin{tabular}{llll}
% \toprule
%         relation & \% types & \% tokens & av. depth \\
% \midrule
%  co-hyponymy (closure, max depth=10) &  0.889 &  0.551 &       3.479 \\
%     hyponymy (closure, max depth=10) &  0.097 &  0.328 &       2.204 \\
%         synonymy &  0.015 &  0.121 &       1.000 \\
% \bottomrule
% \end{tabular}

\begin{tabular}{l|ll|ll|ll|ll|ll}
\toprule
      & \multicolumn{2}{c}{crossclassified} & \multicolumn{2}{c}{co-hyponymy} & \multicolumn{2}{c}{hypernymy} & \multicolumn{2}{c}{not-covered} & \multicolumn{2}{c}{synonymy} \\
         domain & typ & tok & typ & tok & typ & tok & typ &  tok & typ & tok \\
\midrule
 people &  0.725 &  0.618 &  0.019 &  0.032 &  0.051 &  0.293 &  0.200 &  0.038 &  0.005 &  0.019 \\
 clothing &  0.709 &  0.661 &  0.020 &  0.046 &  0.045 &  0.195 &  0.219 &  0.085 &  0.008 &  0.012 \\
 animals\_plants &  0.679 &  0.461 &  0.032 &  0.102 &  0.111 &  0.365 &  0.167 &  0.058 &  0.011 &  0.014 \\
 food &  0.590 &  0.433 &  0.031 &  0.033 &  0.104 &  0.432 &  0.267 &  0.089 &  0.009 &  0.013 \\
 vehicles &  0.635 &  0.329 &  0.026 &  0.083 &  0.059 &  0.239 &  0.271 &  0.089 &  0.008 &  0.260 \\
 home &  0.672 &  0.644 &  0.026 &  0.072 &  0.040 &  0.130 &  0.254 &  0.097 &  0.009 &  0.057 \\
 buildings &  0.780 &  0.725 &  0.026 &  0.038 &  0.045 &  0.156 &  0.138 &  0.058 &  0.011 &  0.022 \\
 \hline
 all &  0.731 &  0.574 &  0.033 &  0.057 &  0.076 &  0.256 &  0.147 &  0.050 &  0.013 &  0.064 \\
\bottomrule
\end{tabular}

\caption{Lexical relations between naming variants according to WordNet, for the set of name pairs where both words can be found in WordNet and stand in a \sz{should we produce this table for the different domains?} \gbt{yes, please. Maybe do rows domains, columns lexical relations (synymymy, hyponymy, co-hyponymy, other, not in wordnet), with subcolumns for types and tokens? And do percentages over rows -- for each domain, how many of the variants we find fall into each of the classes. This way we'll be able to see differences across domains.}}
\label{tab:rel}
\end{table*}
